{\sf NodIO}, a JavaScript framework for volunteer-based evolutionary algorithms : first results

### 2016-01-07 special-issue-ci/volunteer-clouds-ieee-ci-si-tr.tex
A few changes here and there

\title{{\sf NodIO}, a framework for evolutionary algorithms in JavaScript: first results}

%(Mario) Maybe:  {\sf NodIO}, a JavaScript framework for volunteer-based evolutionary algorithms.

@@

JavaScript is an interpreted language mainly known for its inclusion
as an embedded language for programming web browsers. This has
inspired its use, for a long time, as a tool for evolutionary
algorithms, mainly so in browser-based volunteer computing
environments. Several libraries have also been published so far and are in
use. However, the last years have seen a resurgence of interest in the
language, becoming one of the most popular and thus spawning the
improvement of its implementations, which are now the foundation of many
new client-server applications. We present such an application for
running distributed volunteer-based evolutionary algorithm 
experiments, and we make a series of
measurements to establish the speed of JavaScript in evolutionary
algorithms that can serve as a baseline for comparison with other
distributed computing experiments. These experiments use different
integer and floating point problems, and prove that the speed of
JavaScript is actually competitive with other languages commonly used
by the evolutionary algorithm practitioner.

>>>>

\title{{\sf NodIO}, a JavaScript framework for volunteer-based evolutionary algorithms : first results}

%(Mario) Maybe:  {\sf NodIO}, a JavaScript framework for
%volunteer-based evolutionary algorithms.
% Accepted with a small change :-) - JJ

@@

JavaScript is an interpreted language mainly known for its inclusion
in web browsers, making them a container for rich Internet based applications. This has
inspired its use, for a long time, as a tool for evolutionary
algorithms, mainly so in browser-based volunteer computing
environments. Several libraries have also been published so far and are in
use. However, the last years have seen a resurgence of interest in the
language, becoming one of the most popular and thus spawning the
improvement of its implementations, which are now the foundation of many
new client-server applications. We present such an application for
running distributed volunteer-based evolutionary algorithm 
experiments, and we make a series of
measurements to establish the speed of JavaScript in evolutionary
algorithms that can serve as a baseline for comparison with other
distributed computing experiments. These experiments use different
integer and floating point problems, and prove that the speed of
JavaScript is actually competitive with other languages commonly used
by the evolutionary algorithm practitioner.
